Self Regulation Ontology Retest Analyses

### 2018-08-10 code/SRO_Retest_Analyses.Rmd
cleaned up lit review figure

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'bottom',
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20), 
        legend.text = element_text(size=12), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=20),
        legend.spacing.x = unit(0.5, "inches")) + 
  guides(size = guide_legend(override.aes = list(size=c(9,18,28))),
         shape = guide_legend(override.aes = list(size=18)))+
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3), name="Type")+
  scale_size_continuous(name = "Sample Size")+
  geom_vline(xintercept = 0, color = "red", size = 1)

p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
```

>>>>

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'bottom',
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20), 
        legend.text = element_text(size=16), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=20),
        legend.spacing.x = unit(0.5, "inches"),
        legend.box = "vertical",
        legend.direction = "horizontal") + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15), name="Type")+
  scale_size_continuous(name = "Sample Size", 
                        limits = c(10, 1200),
                        range = c(1, 40), 
                        breaks = c(10, 100, 1000))+
  guides(#size = guide_legend(override.aes = list(breaks = c(10, 100, 1000)), labels = c(10, 100, 1000)),
         shape = guide_legend(override.aes = list(size = 16)))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = sort(unique(lit_review$type)), values = c(17, 3, 16, 15))+
  scale_size_continuous(range = c(1, 40),
                        limits = c(10,1200))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme(axis.text.y = element_text(size=30),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 15))+
  scale_shape_manual(breaks = c("ICC","Pearson","Spearman"), 
                     values = c(17, 16, 15))+
  scale_size_continuous(range = c(1, 40),
                        limits = c(10,1200))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 72)
```

```{r}
lit_review %>%
  select(dv, sample_size, task) %>%
  ggplot(aes(sample_size, fill=task))+
  geom_histogram(position = "identity", alpha = 0.5)

rm(p1_t, p2_t, p3_t, mylegend, p1_t_legend)
```
